---
output: pdf_document
---
# ToothGrowth Analysis

* Load the ToothGrowth data and perform some basic exploratory data analyses 
```{r}
suppressMessages(library(datasets))
suppressMessages(library(ggplot2))
suppressMessages(library(dplyr))
data(ToothGrowth)
str(ToothGrowth)
```

```{r}
ToothGrowth
```

Length of ToothGrowth$len 
```{r}
length(ToothGrowth$len)
```


Mean of ToothGrowth Dataset
```{r}
aggregate(ToothGrowth$len,list(ToothGrowth$supp,ToothGrowth$dose),mean)
```

Standard Deviation of ToothGrowth Dataset
```{r}
aggregate(ToothGrowth$len,list(ToothGrowth$supp,ToothGrowth$dose),sd)
```

BoxPlot of the quantile
```{r}
    ggplot(ToothGrowth, aes(x = factor(dose), y = len, fill = factor(dose)))+
                  geom_boxplot()+
                  facet_grid(.~supp)+
                  labs(title = "Tooth Length vs. OJ & VC type Dose",
                  x = "Doses #", y = "Tooth Length") 

```

* Provide a basic summary of the data.

```{r}
summary(ToothGrowth)
```

* Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

If we refer to the box plot , OJ seems better with 0.5 dose and 1 which effects on the teeth growth than VC. We can assume by making hypothesis that mean of OJ and VC will not more than 0

<b>a) 0.5 Dose</b><br>

With 0.95% confident rate , the boundary of from <b>1.719057</b> and <b>8.780943</b> contains the difference between the two population. Because of the boundary does not have 0 value , the possibility that the two population means are <b style="color:red">not equal</b>.

```{r}
oj_dose95 <- ToothGrowth %>% filter(dose=="0.5" & supp=="OJ")
vc_dose95 <- ToothGrowth %>% filter(dose=="0.5" & supp=="VC")
t.test(oj_dose95$len,vc_dose95$len)

```

<b>b) 1 Dose</b><br>

With 0.95% confident rate , the boundary of from <b>2.802148</b> and <b>9.057852</b> contains the difference between the two population. Because of the boundary does not have 0 value , the possibility that the two population means are <b style="color:red">not equal</b>.

```{r}
oj_dose95 <- ToothGrowth %>% filter(dose=="1" & supp=="OJ")
vc_dose95 <- ToothGrowth %>% filter(dose=="1" & supp=="VC")
t.test(oj_dose95$len,vc_dose95$len)
```

<b>c) 2 Dose</b><br>

With 0.95% confident rate , the boundary of from <b>-3.79807</b> and <b>3.63807</b> contains the difference between the two population. Because of the boundary does not have 0 value , the possibility that the two population means <b style="color:green">are equal</b>.

```{r}
oj_dose95 <- ToothGrowth %>% filter(dose=="2" & supp=="OJ")
vc_dose95 <- ToothGrowth %>% filter(dose=="2" & supp=="VC")
t.test(oj_dose95$len,vc_dose95$len)
```

* State your conclusions and the assumptions needed for your conclusions. 

We can conclude that With 95% rate confident , OJ dose with 0.5 and 1  will have <b style="color:green">longer tooth length </b> than VC with the same 0.5 and 1 dose. 
We also can assume with the dose of 2 , there is <b style="color:red">no significant different</b> effects between for both OV and VC.


